### 2020-07-14 paper/sections/design.tex
response letter and revision

\begin{algorithm}[!t]
	\caption{Training RL agent $ \phi $ in environment $ \{\mathcal{X}, M\} $}
	\label{alg: rl-train}
	\begin{algorithmic}[1]
		\STATE Initialize replay memory buffer $ \mathcal{D} $ to capacity $ N $
		\STATE Initialize \emph{action-value function} $ Q $ with random weights $ \theta $
		\STATE Initialize sequence $ s_1 = \mathcal{E}\big(J(x_1, c_1)\big), x_1 \in \mathcal{X} $ and $ \phi_1 = \phi(f_1) $
		\FOR {$t \in 1,2,\cdots, K$}
		\STATE \textbf{1) Exploration.} With probability $\epsilon$:
		\STATE \hspace{1em} $c_t \leftarrow$ a random valid value 
		\STATE Otherwise:
		\STATE \hspace{1em} $ c_t \leftarrow {\rm argmax}_cQ\Big(\phi\big(\mathcal{E}(f_t)\big), c; \theta\Big) $

@@

		\STATE \textbf{2) Reward calcuation.} 
		\STATE Compress image $ x_t $ at quality $ c_t $ to upload
		\STATE Receive $ (\vec{y}_{\rm ref}, \vec{y}_c) $ from the cloud service
		\STATE $ r \leftarrow R(\Delta s, \mathcal{A}_c) $

		\STATE 
		\STATE \textbf{3) Gradient decent.} Generate $ c_t, x_{t+1} $
		\STATE $ s_{t+1} \leftarrow s_t $, $ \phi_{t+1} \leftarrow \phi \big(\mathcal{E}(f_{t+1})\big) $
		\STATE $ \mathcal{D} \leftarrow \mathcal{D} \bigcup \{(\phi_t, c_t, r_t, \phi_{t+1}) \} $
		\IF {$ t \mod T = 0 $ and $ t \geq T_{\rm start} $}
		\STATE Sample a randomly mini-batch of transitions \\ $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
		\STATE $ y_i \leftarrow r_j + \gamma \max_{c'}Q(\phi_{j+1}, c'; \theta) $
		\STATE Compute decay exploration rate \\
		$ \epsilon \leftarrow 
		\begin{cases}
		\mu_{\rm dec}\cdot \epsilon & \text{ if } \ \mu_{\rm dec}\cdot \epsilon > \epsilon_{\min} \\ 
		\epsilon_{\min}             & \text{ if } \ \mu_{\rm dec}\cdot \epsilon \leq \epsilon_{\min}
		\end{cases} $
		\STATE Perform a gradient descent step on \\ $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
		\ENDIF
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

@@

In our solution, the agent is trained by the reward feedback from the environment $ \{\mathcal{X}, M\} $. In the above formulation, we define compression rate $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $ at compression quality level $ c $. Basically, we want the agent to choose a proper compression quality level for minimizing the upload image size while remaining acceptable accuracy. Therefore the overall reward $ r $ should be in proportion to the accuracy $ \mathcal{A} $ while in inverse proportion to the compression ratio $ \Delta s $. We introduce two linear factors $ \alpha $ and $ \beta $ to form a linear combination $ r = \alpha \mathcal{A} - \Delta s + \beta $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $. %% \\

\subsection{Inference-Estimation-Querying-Retraining Mechanism}

@@

\begin{align*}
\bar{\mathcal{A}_n} &=
\begin{cases}
\frac{1}{n}\sum_{i=N-n}^{N} \mathcal{A}_i & \text{ if } N \geq n \\ 
\frac{1}{n}\sum_{i=1}^{n} \mathcal{A}_i & \text{ if } N < n 
\end{cases}
\end{align*}

With this definition, an intuitive formulation of the change of $ p_{\rm est} $ is in inverse proportion of the gradient of $ \mathcal{A} $, meaning that when the recent accuracy decreases, the estimation probability $ p_{\rm est} $ would increase. We define that $ p'_{\rm est} = p_{\rm est} + \omega \nabla \bar{\mathcal{A}} $ where $ \omega $ is a scaling factor. With this recursive formula, we have the general term of $p_{\rm est} = p_0 + \omega \sum_{i=0}^{N} \nabla \bar{\mathcal{A}_i} $ where $ p_0 $ is an initial estimation probability.

@@

In our experiment, we find that in different cloud-based application environments, the agent's chosen compression quality levels can be quite different. As shown in Figure~\ref{fig: quality_chosen}, for Face++ and Amazon Rekognition, the agent's choices are concentrated at around $ c=15 $, but for Baidu Vision, the agent's selections are distributed more evenly. The ``optimal'' compression strategies are different for different backend cloud services. This variation is caused by the interaction between the agent and the backend cloud model in the training phase. Since the agent's training procedure is based on a specific backend cloud model $ M_1 $, for another backend cloud model $ M_2 $, the interaction between the agent and $ M_2 $ is quite different. Therefore the agent's best compression quality level selection presents variation for different backend cloud models.

\begin{figure}[!t]
	\includegraphics[width=0.8\linewidth]{figures/quality_chosen.pdf}
	\caption{Histogram of RL agent's best compression quality level selection for different cloud services}
	\label{fig: quality_chosen}
	% \vspace{-0.3cm}
\end{figure}

Moreover, in our experiment, the agent presents different behaviors when the input image changes from one dataset to another. Figure~\ref{fig: dataset_change} shows the agent's choices for the same backend cloud model (Baidu Vision) but different image datasets. We prepare two datasets indicating two contextual ``sceneries''. We randomly sample images from ImageNet~\cite{ImageNet} whose images are mostly taken in the daytime, to act as a daytime scenery, and randomly select nighttime images from the FLIR Thermal Dataset~\cite{FLIR} to form another dataset to act as a nighttime scenery. The histogram shown in Figure~\ref{fig: dataset_change} points out that, for the ImageNet images, the agent prefers a low compression quality level, but its choices are distributed more evenly. For the FLIR Thermal images, the agent's choices are more accumulated in some relatively higher compression quality levels. We can see that, to maintain high accuracy, when the input image's contextual group $ \mathcal{X} $ changes, the agent's compression quality level selection would change as well. This phenomenon presents that the agent can adaptively choose a proper compression quality level based on the input image's features. %% \\

\begin{figure}[!t]
    \includegraphics[width=0.8\linewidth]{figures/dataset_change.pdf}
    \caption{Histogram of RL agent's best compression level selection for different scenery image inputs}
    \label{fig: dataset_change}
\end{figure}

%\begin{figure}[!t]
%	\includegraphics[width=\linewidth]{figures/dataset_change.pdf}
%	\caption{Histogram of RL agent's best compression quality level selection for different input image ``sceneries''}
%	\label{fig: dataset_change}
%\end{figure}

>>>>

\begin{algorithm}[!t]
	\caption{Training RL agent $ \phi $ in environment $ \{\mathcal{X}, M\} $}
	\label{alg: rl-train}
	\begin{algorithmic}[1]
		\STATE Initialize replay memory buffer $ \mathcal{D} $ to capacity $ N $
		\STATE Initialize \emph{action-value function} $ Q $ with random weights $ \theta $
		\STATE Initialize sequence $ s_1 = \mathcal{E}\big(J(x_1, c_1)\big), x_1 \in \mathcal{X} $ and $ \phi_1 = \phi(f_1) $
		\FOR {$t \in 1,2,\cdots, K$}
%		\STATE \textbf{1) Exploration.} %With probability $\epsilon$:
		{\color{revise}\STATE \textbf{1) Exploration}}
		{\color{revise}\STATE With probability $\epsilon$:}
		\STATE \hspace{1em} $c_t \leftarrow$ a random valid value 
		\STATE Otherwise:
		\STATE \hspace{1em} $ c_t \leftarrow {\rm argmax}_cQ\Big(\phi\big(\mathcal{E}(f_t)\big), c; \theta\Big) $

@@

%		\STATE \textbf{2) Reward calcuation.} 
		{\color{revise}\STATE \textbf{2) Reward calcuation}} 
		\STATE Compress image $ x_t $ at quality $ c_t $ to upload
		\STATE Receive $ (\vec{y}_{\rm ref}, \vec{y}_c) $ from the cloud service
		\STATE $ r \leftarrow R(\Delta s, \mathcal{A}_c) $

		\STATE 
%		\STATE \textbf{3) Gradient decent.} %Generate $ c_t, x_{t+1} $
		{\color{revise}\STATE \textbf{3) Gradient decent}}
		{\color{revise}\STATE Generate $ c_t, x_{t+1} $}
		\STATE $ s_{t+1} \leftarrow s_t $, $ \phi_{t+1} \leftarrow \phi \big(\mathcal{E}(f_{t+1})\big) $
		\STATE $ \mathcal{D} \leftarrow \mathcal{D} \bigcup \{(\phi_t, c_t, r_t, \phi_{t+1}) \} $
		\IF {$ t \mod T = 0 $ and $ t \geq T_{\rm start} $}
%		\STATE Sample a randomly mini-batch of transitions \\ $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
		{\color{revise}
		\STATE Sample a randomly mini-batch of transitions $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
		\STATE $ y_i \leftarrow r_j + \gamma \max_{c'}Q(\phi_{j+1}, c'; \theta) $
		\STATE Compute decay exploration rate 
		$ \epsilon \leftarrow 
		\begin{cases}
		\mu_{\rm dec}\cdot \epsilon & \text{ if } \ \mu_{\rm dec}\cdot \epsilon > \epsilon_{\min} \\ 
		\epsilon_{\min}             & \text{ if } \ \mu_{\rm dec}\cdot \epsilon \leq \epsilon_{\min}
		\end{cases} $
		\STATE Perform a gradient descent step on $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
		}
%		\STATE Perform a gradient descent step on \\ $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
		\ENDIF
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

@@

In our solution, the agent is trained by the reward feedback from the environment $ \{\mathcal{X}, M\} $. In the above formulation, we define compression rate $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $ at compression quality level $ c $. Basically, we want the agent to choose a proper compression quality level for minimizing the upload image size while remaining acceptable accuracy. \textcolor{revise}{Therefore the overall reward $ r $ should be positively correlated with the accuracy $ \mathcal{A} $ while negatively with the compression ratio $ \Delta s $.} We introduce two linear factors $ \alpha $ and $ \beta $ to form a linear combination $ r = \alpha \mathcal{A} - \Delta s + \beta $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $. %% \\

% Therefore the overall reward $ r $ should be in proportion to the accuracy $ \mathcal{A} $ while in inverse proportion to the compression ratio $ \Delta s $.
\subsection{Inference-Estimation-Querying-Retraining Mechanism}

@@

\begin{align*}
\bar{\mathcal{A}_n} &=
\begin{cases}
%\frac{1}{n}\sum_{i=N-n}^{N} \mathcal{A}_i & \text{ if } N \geq n \\ 
%\frac{1}{n}\sum_{i=1}^{n} \mathcal{A}_i & \text{ if } N < n 
{\color{revise}\frac{1}{n}\sum_{i=N-n+1}^{N} } \mathcal{A}_i & \text{ if } N \geq n \\ 
{\color{revise}\frac{1}{N}\sum_{i=1}^{N} }\mathcal{A}_i & \text{ if } N < n 
\end{cases}
\end{align*}

With this definition, \textcolor{revise}{the change of $ p_{\rm est} $ should be negatively correlated with} the gradient of $ \mathcal{A} $, meaning that when the recent accuracy decreases, the estimation probability $ p_{\rm est} $ would increase. We define that $ p'_{\rm est} = p_{\rm est} + \omega \nabla \bar{\mathcal{A}} $ where $ \omega $ is a \textcolor{revise}{negative} scaling factor. With this recursive formula, we have the general term of $p_{\rm est} = p_0 + \omega {\color{revise}\sum_{i=1}^{N}} \nabla \bar{\mathcal{A}_i} $ where $ p_0 $ is an initial estimation probability.

% an intuitive formulation of % is in inverse proportion of
% \sum_{i=0}^{N}

@@

\textcolor{revise}{As shown in Figure~\ref{fig: quality_chosen}, we find that in different cloud-based application environments, the agent's chosen compression quality levels can be quite different. We compute the \emph{mean} and \emph{standard deviation} of compression quality levels. The mean is respectively 33.4, 24.7 and 31.6 on Baidu Vison, Face++ and Amazon Rekognition. For Face++, the \emph{mean} of compression quality levels is lower than that for Baidu Vision. The standard deviation is respectively 22.77, 19.19 and 22.46 on Baidu Vison, Face++ and Amazon Rekognition.} The ``optimal'' compression strategies are different for different backend cloud services. This variation is caused by the interaction between the agent and the backend cloud model in the training phase. Since the agent's training procedure is based on a specific backend cloud model $ M_1 $, for another backend cloud model $ M_2 $, the interaction between the agent and $ M_2 $ is quite different. Therefore the agent's best compression quality level selection presents variation for different backend cloud models.

%In our experiment, we find that in different cloud-based application environments, the agent's chosen compression quality levels can be quite different. As shown in Figure~\ref{fig: quality_chosen}, for Face++ and Amazon Rekognition, the agent's choices are concentrated at around $ c=15 $, but for Baidu Vision, the agent's selections are distributed more evenly.

\begin{figure*}[!t]
{\color{revise}
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Baidu_choices1.pdf}}
		\centerline{(a) Baidu Vision}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Facepp_choices1.pdf}}
		\centerline{(b) Face++}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Amazon_choices1.pdf}}
		\centerline{(c) Amazon Rekognition}
	\end{minipage}		
	\caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different cloud services}}
	\label{fig: quality_chosen}
}
\end{figure*}

%\begin{figure}[!t]
%	\includegraphics[width=0.8\linewidth]{figures/quality_chosen.pdf}
%	\caption{Histogram of RL agent's best compression quality level selection for different cloud services}
%	\label{fig: quality_chosen}
%	% \vspace{-0.3cm}
%\end{figure}

Moreover, in our experiment, the agent presents different behaviors when the input image changes from one dataset to another. Figure~\ref{fig: dataset_change} shows the agent's choices for the same backend cloud model (Baidu Vision) but different image datasets. We prepare two datasets indicating two contextual ``sceneries''. We randomly sample images from ImageNet~\cite{ImageNet} whose images are mostly taken in the daytime, to act as a daytime scenery, and randomly select nighttime images from the FLIR Thermal Dataset~\cite{FLIR} to form another dataset to act as a nighttime scenery. \textcolor{revise}{The histogram shown in Figure~\ref{fig: dataset_change} points out that the distribution of compression quality levels is different on ImageNet and FLIR Thermal Dataset. For ImageNet and FLIR, the mean is respectively 43.3 and 47.5, and the standard deviation is respectively 19.52 and 26.56.} We can see that, to maintain high accuracy, when the input image's contextual group $ \mathcal{X} $ changes, the agent's compression quality level selection would change as well. This phenomenon presents that the agent can adaptively choose a proper compression quality level based on the input image's features.

\textcolor{revise}{We can also find that Figure~\ref{fig: quality_chosen}(a) and Figure~\ref{fig: dataset_change}(a) is different, even if we use the same cloud service (Baidu Vision) and image dataset (ImageNet). When we use the same cloud service at different times, the cloud service commonly invokes different backend cloud models. Therefore the interaction between the agent and the backend cloud model is different. This result variation presents that the agent can adaptively make a proper compression strategy in different complex environments, indicating our solution's generality and practicality.} %% \\

%The histogram shown in Figure~\ref{fig: dataset_change} points out that, for the ImageNet images, the agent prefers a low compression quality level, but its choices are distributed more evenly. For the FLIR Thermal images, the agent's choices are more accumulated in some relatively higher compression quality levels.

%\begin{figure}[!t]
%    \includegraphics[width=0.8\linewidth]{figures/dataset_change.pdf}
%    \caption{Histogram of RL agent's best compression level selection for different scenery image inputs}
%    \label{fig: dataset_change}
%\end{figure}

\begin{figure*}[!t]
{\color{revise}
	\begin{minipage}[t]{0.48\linewidth}
		\centerline{\includegraphics[width=7cm]{figures/ImageNet_Baidu_choices.pdf}}
		\centerline{(a) ImageNet images}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.48\linewidth}
		\centerline{\includegraphics[width=7cm]{figures/FLIR_Baidu_choices.pdf}}
		\centerline{(b) FLIR images}
	\end{minipage}	
    \caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different scenery image inputs}}
	\label{fig: dataset_change}
}
\end{figure*}

### 2020-07-14 paper/sections/evaluation.tex
response letter and revision

\begin{table*}[!t]
	\centering
	\caption{Experiment parameter}
	\label{tab: parameters}
	%     \begin{tabular}{llllll}
	\begin{tabular}{cccccc}
		\toprule
		notation          & value & & & notation     & value  \\ \midrule
		$c_{\rm ref}$ & 75    & & & $K$      & 1000   \\
		$\epsilon_{\min}$    & 0.02  & & & $p_0$    & 0.2    \\
		$\gamma$      & 0.95  & & & $\omega$ & -3   \\
		$ \mu_{\rm dec} $ & 0.99 & & & $ T $ & 5  \\
		$r_{\rm th}$  & 0.45   & & &   $ n  $  &  10      \\ \bottomrule
	\end{tabular}
%	\vspace{-0.5cm}
\end{table*}

@@

Comparing to the conventional solution that uploads the image directly, in our solution, the image is passed to the RL agent firstly to estimate the compression quality level. Running this RL agent brings extra latency to the whole system. In this subsection, we evaluate the overall latency overhead. %% \\

We compute compressed file size for batches of images, and test the RL agent's inference time and the latency of uploading such compressed images. We test the average inference latency on 1000 ImageNet images and simulate the network bandwidth as 27.64 Mbps according to the global average fixed broadband upload speed~\cite{speedtest} in Feb. 2019, to verify the end-to-end latency performance. The latency comparison is listed in Table~\ref{tab: latency-overhead}. %% \\

\begin{table*}[!t]
	\centering
	\caption{Latency between image upload and inference result feedback}
	\label{tab: latency-overhead}
	%     \begin{tabular}{lll}
	\begin{tabular}{ccc}
		\toprule
		& Benchmark & AdaCompress  \\ \midrule
		Average upload size          & 42.68 KB  &  18.46 KB            \\
		Inference latency    & 0 s       & 2.09 ms          \\
		Transmission latency & 12.35 ms       & 5.34 ms          \\
		Overall latency      & 12.35 ms       & 7.43 ms          \\ \bottomrule
	\end{tabular}
	% \vspace{-0.5cm}
\end{table*}

Our solution brings in inference latency to the end-to-end latency, but the transmission latency is low by reducing the upload file size. In today's network architecture where the edge infrastructure's computational power is increasing significantly ~\cite{satyanarayanan2017emergence,hu2015mobile}, we can use the computing power of the edge infrastructure in exchange for the reduction of upload traffic load and transmission latency. %% \\

>>>>

\begin{table*}[!t]
	\centering
	\caption{Experiment parameter}
	\label{tab: parameters}
	%     \begin{tabular}{llllll}
	\begin{tabular}{cccccc}
		\toprule
		Notation          & Value & & & Notation     & Value  \\ \midrule
		$c_{\rm ref}$ & 75    & & & $K$      & 1000   \\
		$\epsilon_{\min}$    & 0.02  & & & $p_0$    & 0.2    \\
		$\gamma$      & 0.95  & & & $\omega$ & -3   \\
		$ \mu_{\rm dec} $ & 0.99 & & & $ T $ & 5  \\
		$r_{\rm th}$  & 0.45   & & &   $ n  $  &  10      \\ 
		{\color{revise} $ \mathcal{A}_0 $} & {\color{revise}0.8} & & & {\color{revise}$ T_{\rm start} $} & {\color{revise}128} \\
		$ {\color{revise}\alpha} $ & {\color{revise}1} & & & {\color{revise}$ \beta $} & {\color{revise}1}  \\ \bottomrule
	\end{tabular}
	%	\vspace{-0.5cm}
\end{table*}

%\begin{table*}[!t]
%	\centering
%	\caption{Experiment parameter}
%	\label{tab: parameters}
%	%     \begin{tabular}{llllll}
%	\begin{tabular}{cccccc}
%		\toprule
%		Notation          & Value & & & Notation     & Value  \\ \midrule
%		$c_{\rm ref}$ & 75    & & & $K$      & 1000   \\
%		$\epsilon_{\min}$    & 0.02  & & & $p_0$    & 0.2    \\
%		$\gamma$      & 0.95  & & & $\omega$ & -3   \\
%		$ \mu_{\rm dec} $ & 0.99 & & & $ T $ & 5  \\
%		$r_{\rm th}$  & 0.45   & & &   $ n  $  &  10      \\ \bottomrule
%	\end{tabular}
%%	\vspace{-0.5cm}
%\end{table*}

@@

Comparing to the conventional solution that uploads the image directly, in our solution, the image is passed to the RL agent firstly to estimate the compression quality level. Running this RL agent brings extra latency to the whole system. In this subsection, we evaluate the end-to-end latency. %% \\

We compute compressed file size for batches of images, and test the RL agent's inference time and the latency of uploading such compressed images. \textcolor{revise}{We respectively test the average inference latency on 1000 ImageNet images and 1000 FLIR images}, and simulate the network bandwidth as 27.64 Mbps according to the global average fixed broadband upload speed~\cite{speedtest} in Feb. 2019, to verify the end-to-end latency performance. The latency comparison is listed in Table~\ref{tab: latency-overhead}. %% \\

%We compute compressed file size for batches of images, and test the RL agent's inference time and the latency of uploading such compressed images. We test the average inference latency on 1000 ImageNet images and simulate the network bandwidth as 27.64 Mbps according to the global average fixed broadband upload speed~\cite{speedtest} in Feb. 2019, to verify the end-to-end latency performance. The latency comparison is listed in Table~\ref{tab: latency-overhead}. %% \\

\begin{table*}[!t]
{\color{revise}
	\centering
	\caption{\textcolor{revise}{Latency of edge device to cloud service}}
	\label{tab: latency-overhead}
	%     \begin{tabular}{lll}
	\resizebox{\textwidth}{!}{
	\begin{tabular}{cccccc}
		\toprule
		Dataset & Solution & Average upload size & Inference latency \
		& Transmission latency & End-to-end latency \\ \midrule
		ImageNet & Benchmark & 42.68 KB & 0 ms & 12.35 ms & 12.35 ms \\
		ImageNet & AdaCompress & 18.64 KB & 2.09 ms & 5.34 ms & 7.43 ms \\
		FLIR & Benchmark & 44.66 KB & 0 ms & 12.93 ms & 12.93 ms \\
 		FLIR & AdaCompress & 17.07 KB & 2.03 ms & 4.94 ms & 6.97 ms \\ \bottomrule
	\end{tabular}}
	% \vspace{-0.5cm}
}
\end{table*}
%\begin{table*}[!t]
%	\centering
%	\caption{Latency between image upload and inference result feedback}
%	\label{tab: latency-overhead}
%	%     \begin{tabular}{lll}
%	\begin{tabular}{ccc}
%		\toprule
%		& Benchmark & AdaCompress  \\ \midrule
%		Average upload size          & 42.68 KB  &  18.46 KB            \\
%		Inference latency    & 0 s       & 2.09 ms          \\
%		Transmission latency & 12.35 ms       & 5.34 ms          \\
%		Overall latency      & 12.35 ms       & 7.43 ms          \\ \bottomrule
%	\end{tabular}
%	% \vspace{-0.5cm}
%\end{table*}

Our solution brings in inference latency to the end-to-end latency, but the transmission latency is low by reducing the upload file size. In today's network architecture where the edge infrastructure's computational power is increasing significantly~\cite{satyanarayanan2017emergence,hu2015mobile}, we can use the computing power of the edge infrastructure in exchange for the reduction of upload traffic load and transmission latency. \textcolor{revise}{Compared with the benchmark solution, our solution effectively reduces the end-to-end latency on both ImageNet and FLIR dataset.} %% \\

\subsection{\textcolor{revise}{Overall Memory and Latency Overhead}}

\subsubsection{\textcolor{revise}{Memory Overhead:}}
\textcolor{revise}{The memory overhead is divided into two parts: the static occupied memory space and dynamic memory usage. Firstly, the static occupied memory space is the memory of the model's size. We use Keras to construct and save MobileNetV2 and the RL agent. We check file size of the saved model as the model's size. A RL agent model's size is 1 MB, and the feature extractor MobileNetV2's size is 8.9 MB. The model caching library stores the most recent five RL agents. The overall memory of the model's size is at most 13.9 MB. Secondly, the dynamic memory usage is the memory usage during AdaCompress runs. The overall memory usage mainly includes the memory buffer of transitions and the memory usage caused by the RL agent and feature extractor. When caching transitions of 1000 images in the memory buffer, it occupies about 500 KB. We use Psutil to measure the peak memory usage during AdaCompress runs. The peak memory usage is about 367 MB. Thirdly, in real-world edge-application scenarios, common edge infrastructures have enough memory to deploy this algorithm, such as Raspberry Pi 4 Model B's \cite{Raspberry-Pi} memory is 2/4/8 GB, and Huawei Atlas 500 edge station's memory is 4/8 GB.}

\subsubsection{\textcolor{revise}{Training and Re-loading Latency:}}
\textcolor{revise}{Although AdaCompress can be highly efficient to run on today's edge infrastructures, it would cause extra latency overhead, such as training and re-loading latency. In this subsection, we evaluate the latency overhead.}

%\begin{table*}[!t]
%	\centering
%	\caption{Time cost of training}
%	\label{tab: training-time}
%		\begin{tabular}{cccc}
%			\toprule
%			Dataset & Number of training images & Time cost & Real time cost \\ \midrule
%			ImageNet & 898 & 15.86 min & 7.89 min \\
%			FLIR & 910 & 15.63 min & 7.85 min \\ \bottomrule
%	\end{tabular}
%	% \vspace{-0.5cm}
%\end{table*}

\textcolor{revise}{In our experiments, the convergence condition of training is that the recent average accuracy over 0.8 meanwhile the recent average reward over 0.45. The experiment results show the number of training images is respectively 898 and 910 on ImageNet and FLIR. The time cost mainly depends on the frequency of sending images and the inference speed of the cloud service. If the end-user sends images continuously, and cloud service's inference speed is about 10 images per second, the time costs are respectively about 197.3s and 200.8s on ImageNet and FLIR. In the training phase, we need to upload reference images and compressed images. We consider the time cost of uploading reference images and obtaining the feedbacks as the benchmark latency. If we minus this benchmark latency, the real training time cost is not over 100s. It is worth to spend such upload size overhead and time cost at the beginning when we need to infer thousands of images.}

%And the training time respectively is 15.36 min and 15.63 min on ImageNet and FLIR.

\textcolor{revise}{The \emph{inference-estimation-querying-retraining} mechanism would either re-load or re-train a RL agent intelligently when capturing the scenery change. The re-training time cost is similar to the training time cost which is described above. The latency of re-loading a RL agent model is about 1.85s. To \emph{erase} this latency, we use another process to re-load the model in our experiments. The mechanism still uses the old RL agent to choose a compression quality level before the re-loading process has finished.}

### 2020-07-14 paper/sections/introduction.tex
response letter and revision

$\rhd$ We design an interactive training environment that can be applied to different online computer vision-based services. We propose a Deep Q-learning Network-based~\cite{DQN} agent to evaluate and predict the performance of a compression quality level on an input image. In real-world application scenarios, this agent can be highly efficient to run on today's edge infrastructures (e.g., Google edge TPU~\cite{google-tpu}, Huawei Atlas 500 edge station~\cite{huawei-atlas500}).

$\rhd$ We build a reinforcement learning-based framework to train the agent in the above environment. The agent can learn to choose a proper compression quality level for an input image after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and data size. We further propose an \emph{explore-exploit} mechanism to let the agent switch between ``sceneries''. In particular, after deploying the agent, an \emph{inference-estimation-querying-retraining} solution is designed to switch the RL agent intelligently once the scenery changes and the existing running agent cannot guarantee the original accuracy performance.
%re-load or re-train a RL agent intelligently
%restart the training
%Based on~\cite{2019adacompress},

$\rhd$~~In this journal extension, we provide more analysis and insights on our design. We notice that the Deep Q-learning Network-based agent's behaviors are various for different input image “sceneries” and backend cloud services. By analyzing the agent's behaviors using Grad-Cam~\cite{grad-cam}, we provide the reasons that the agent chooses a specific compression quality level. We reveal that images containing large smooth areas are more sensitive to compression, while images with complex textures are more robust to compression for computer vision models.

$\rhd$ We evaluate our system on representative cloud-based deep learning services, including Amazon Rekognition~\cite{amazon_rekognition}, Face++~\cite{face++_service} and Baidu Vision~\cite{baidu_vision}. We show that our design can reduce the upload traffic load by up to $1/2$ while maintaining comparable overall accuracy. Compared to baseline DeepN-JPEG~\cite{DeepN-JPEG}, the overall accuracy of AdaCompress is $8\%$ higher when they have similar compressed image size.

% \begin{itemize}
% 	\item First, we completed designing agent caching strategy work mentioned in our previous version's future work~\cite{2019adacompress}, adding the model query state in previous inference-estimate-retrain mechanism to avoid unnecessary upload traffic load in the retraining phase. Once capturing the scenery change, comparing to the previous mechanism that retrains from scratch directly, in our new mechanism, AdaCompress switches into model query state and loads a suitable RL agent model, achieving a lower upload traffic load. In the experiment, we use the FLIR Thermal Dataset instead of the previous DNIM Dataset to act as a nighttime scenery since thermal sensors capture gray-scaled thermal images in the nighttime, and the experiment result shows that our design can cut down the uploading file size overhead effectively.
% 	\item Second, for the comparison purpose, we implement the DeepN-JPEG framework according to~\cite{DeepN-JPEG} and evaluate the size reduction and accuracy performance. Our experiment shows that AdaCompress and DeepN-JPEG both decrease the uploading file size overhead more than 1/2, but the inference accuracy of AdaCompress is 8\% higher than that of DeepN-JPEG. Moreover, we provide illustrative image examples to present that AdaCompress compresses images more adaptively to achieve higher accuracy.
% 	\item Last but not least, we re-organize and amend the manuscript significantly to be easier to follow.
% \end{itemize}

>>>>

\item We design an interactive training environment that can be applied to different online computer vision-based services. We propose a Deep Q-learning Network-based~\cite{DQN} agent to evaluate and predict the performance of a compression quality level on an input image. In real-world application scenarios, this agent can be highly efficient to run on today's edge infrastructures (e.g., Google edge TPU~\cite{google-tpu}, Huawei Atlas 500 edge station~\cite{huawei-atlas500}).
%$\rhd$	
\item We build a reinforcement learning-based framework to train the agent in the above environment. The agent can learn to choose a proper compression quality level for an input image after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and data size. We further propose an \emph{explore-exploit} mechanism to let the agent switch between ``sceneries''. In particular, after deploying the agent, an \emph{inference-estimation-querying-retraining} solution is designed to switch the RL agent intelligently once the scenery changes and the existing running agent cannot guarantee the original accuracy performance.
%re-load or re-train a RL agent intelligently
%restart the training
%Based on~\cite{2019adacompress},

\item In this journal extension, we provide more analysis and insights on our design. We notice that the Deep Q-learning Network-based agent's behaviors are various for different input image “sceneries” and backend cloud services. By analyzing the agent's behaviors using Grad-Cam~\cite{grad-cam}, we provide the reasons that the agent chooses a specific compression quality level. We reveal that images containing large smooth areas are more sensitive to compression, while images with complex textures are more robust to compression for computer vision models.

\item We evaluate our system on representative cloud-based deep learning services, including Amazon Rekognition~\cite{amazon_rekognition}, Face++~\cite{face++_service} and Baidu Vision~\cite{baidu_vision}. We show that our design can reduce the upload traffic load by up to $1/2$ while maintaining comparable overall accuracy. Compared to baseline DeepN-JPEG~\cite{DeepN-JPEG}, the overall accuracy of AdaCompress is $8\%$ higher when they have similar compressed image size.
\end{itemize}
% \begin{itemize}
% 	\item First, we completed designing agent caching strategy work mentioned in our previous version's future work~\cite{2019adacompress}, adding the model query state in previous inference-estimate-retrain mechanism to avoid unnecessary upload traffic load in the retraining phase. Once capturing the scenery change, comparing to the previous mechanism that retrains from scratch directly, in our new mechanism, AdaCompress switches into model query state and loads a suitable RL agent model, achieving a lower upload traffic load. In the experiment, we use the FLIR Thermal Dataset instead of the previous DNIM Dataset to act as a nighttime scenery since thermal sensors capture gray-scaled thermal images in the nighttime, and the experiment result shows that our design can cut down the uploading file size overhead effectively.
% 	\item Second, for the comparison purpose, we implement the DeepN-JPEG framework according to~\cite{DeepN-JPEG} and evaluate the size reduction and accuracy performance. Our experiment shows that AdaCompress and DeepN-JPEG both decrease the uploading file size overhead more than 1/2, but the inference accuracy of AdaCompress is 8\% higher than that of DeepN-JPEG. Moreover, we provide illustrative image examples to present that AdaCompress compresses images more adaptively to achieve higher accuracy.
% 	\item Last but not least, we re-organize and amend the manuscript significantly to be easier to follow.
% \end{itemize}
